---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
    font-family: 'Roboto', sans-serif;
    background-color: #f4f7fc;
    color: #333;
    margin: 0;
    padding: 20px;
}

h2 {
    text-align: center;
    color: #2c3e50;
    font-size: 24px;
}
```

## Observational Logging of Phone Checking Behaviour

Using a designed survey, I recorded information about each time I checked my phone. The collected data reveals insights about the purpose of checking, screen time, distraction patterns and the impact of notifications.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQMjGhy5aXOstY_APwzqO0mLl79bJ8_ruF33EFXWQrGkQLVtLILHdMHacXDgj26l94s_LiHdnC3mYOj/pub?output=csv") %>%
  rename(primary_reason = 2,
          notification = 3,
          screen_time = 4,
          distracted = 5)

latest_data <- logged_data %>%
  select(primary_reason, notification, screen_time, distracted)

mean_screen_time <- mean(latest_data$screen_time)

max_screen_time <- max(latest_data$screen_time)
 
```

Throughout the case study, I spent an average of `r mean_screen_time` minutes per instance of phone use. On one occasion, screen time extended to a maximum of `r max_screen_time` minutes following a single phone check.

The graph below indicates how notifications could affect the phone checking behaviours.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = notification), fill = "#00CED1") +
  labs(title = "The Role of Notifications in Phone Checking",
       subtitle = "Examining whether phone checking was initiated by notifications",
       x = "Notification",
       y = "Times checking the phone")
```

Further, the analysis suggests the patterns of distraction as regards the purposes of checking the phone.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(y = primary_reason, fill = distracted)) +
  labs(title = "Reasons for Phone Checking and Distraction Patterns",
       subtitle = "Examining whether the user focussed on the main reason or got sidetracked",
       x = "Times checking the phone",
       y = "The primary reason")
```